---
title: "Cabbages"
author: "Taylor Stohl"
date: "Summer 2021"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
basicCN <- ggplot(veggy,aes(x=Cult,y=VitC))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
  It appears  based on the graphical data that c52 contains much more vitamin C than c39. The box for c52 is evidently above the box for the c39. The box in the graph represents 50% of the data and the dark black line represents the median of all data collected.
  

### Numerical Descriptive Results


<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->



```{r}
favstats(VitC~Cult,data=veggy)
```
 
 The table shows that c52  on average receives 64.5 IU of vitamin C whereas c39 only receives on average 51.0 IU of vitamin C.

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfies the assumptions and is appropriate to answer the research question!-->

  
```{r}
t.test(VitC~Cult,data=veggy)
```
The p-value is .00000003405 which is a tiny number.The null hypothesis assumes that they have the same amount of vitamin C. We reject the null hypothesis as these two are evidently very different. This number proves that they don't have the same amount of vitamin C. c52 is better than c39 because it consists of more vitamin C.



# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

In our initial variable analysis, it was established that this particular project is a numerical - categorical batch of data I used the numerical-cat file helper to assist me in the project.

The c52 was discovered to have a much higher vitamin C content than c39.
